Monte Carlo Bootstrap: current developments.

### 2019-03-22 draft.tex
added multipoint and expanded Gliozzi review

\section{Review of Gliozzi's paper}
In 2013, \cite{Gliozzi:2013ysa} realized that, for $N_z$ bigger than the number of operators
one considered in the OPE ($N_{Op}$), \ref{matrix-boo} represented an over-determined
Linear System. Thus, in order for a solution (that is, a set of OPE coefficients
satisfying crossing) to exist, each minor should vanish.

\section{LogDet implementation}
\subsection{naive approach}
Given a putative spectrum, the determinant of \ref{matrix-op} (when
$Nz=N_{Op}+1$)
should get closer to zero as we approach a physically sensible set of operator
dimensions. Since this quantity could range over many orders of magnitude, we
decided to square it and then take the $\log$ of it. This proved to be
numerically troubling due to the behaviour of the logarithm around $0$  and the landscape was thus full of spurious minima out of
which the Metropolis algorithm could not get out.

@@

@@

For properly chosen
points in $z$, not all the inequalties in \ref{cross-check} will be satisfied,
one can then take this number and try to minimize it with another Monte Carlo
routine. Concretely, this routine takes the naive $\Delta^*$ and given a certain
number of $z$-points, it counts for how many of these points are the crossing
equations are violated (NoV). It also counts how many zero coefficients are there in
the solution. Then, the optimization proceeds by changing one of the dimensions
whose corresponding OPE coefficients are not zero and then calculating the NoV
and the number of zero coefficients again. If both the NoV and the number of
zero OPE coefficients remain constant or decrease, the move is accepted,
otherwise it is rejected. The optimization terminates when NoV=0 for two
different sets of z points or when a certain number of iterations is attained.

>>>>

\section{Review of Gliozzi's paper}
In 2013, \cite{Gliozzi:2013ysa} realized that, for $N_z$ bigger than the number of operators
one considered in the OPE ($N_{Op}$), \ref{matrix-boo} represented an over-determined
Linear System. Thus, in order for a solution (that is, a set of OPE coefficients
satisfying crossing) to exist, each minor should vanish. More concretely, if one
is trying to find the dimensions of $N$ operators, one should consider $N$
different minors, in order to have $N$ trascendental equations and a (hopefully
non empty)
set of discrete solutions. Then, the error can be estimated by considering a
different set of $N$ minors and seeing how much the solutions change. Although
conceptually clear, this proved to be a major drawback when assesing the
precision of the results obtained with this method.

Gliozzi's approach gives results for the Lee-Yang edge singularity in $2$, $3$
and $4$
dimensions that resemble quite closely the exact ones (for the 2-dimensional
case) and the numerical results obtained for $D=3,4$.

Drawing inspiration from Gliozzi's work we can posit a functional depending on a
very big set of $z-$points and all the possible minors thereof. The solutions to
the crossing equations should then minimize all these determinants.

\section{LogDet implementation}
We now describe the different stages that our Monte Carlo approach followed.
As a testing ground, we started with the minimum amount of $z-$points. Then, we
saw the need of regularizing the numerical singularities that this action had.
We finally implemented an approach that captures Gliozzi's idea of considering
several minors.
\subsection{naive approach}
Given a putative spectrum, the determinant of \ref{matrix-op} (when
$Nz=N_{Op}+1$)
should get closer to zero as we approach a physically sensible set of operator
dimensions. Since this quantity could range over many orders of magnitude, we
decided to square it and then take the $\log$ of it. This proved to be
numerically troubling due to the behaviour of the logarithm around $0$  and the landscape was thus full of spurious minima out of
which the Metropolis algorithm could not get out.

@@

\subsection{Multiminor approach}
Searching to avoid the numerical problems posed by taking only $O(10)$ points from a
distribution, we expanded our $\mathrm{logDet}$ approach to consider a bigger number of
$z-$points, and adjusting the functional to be

\[
\begin{aligned}
  S(\{\Delta_i,l_i\})& = \sum_i \log\Det^2\mathcal{M}_i(\{\Delta_i,l_i\};{z_j}_i)\\
\end{aligned}
\]

@@

For properly chosen
points in $z$, not all the inequalties in \ref{cross-check} will be satisfied.
One can then take this number and try to minimize it with another Monte Carlo
routine. Concretely, this routine takes the naive $\Delta^*$ and given a certain
number of $z$-points, it counts for how many of these points are the crossing
equations are violated (NoV). It also counts how many zero coefficients are there in
the solution. Then, the optimization proceeds by changing one of the dimensions
whose corresponding OPE coefficients are not zero and then calculating the NoV
and the number of zero coefficients again. If both the NoV and the number of
zero OPE coefficients remain constant or decrease, the move is accepted,
otherwise it is rejected. The optimization terminates when NoV=0 for two
different sets of z points or when a certain number of iterations is attained.
